Let N be the population size so, N=120. The given sample size is n.
\textbf{Notations :}
y : student under consideration.
$y_i$ : Maths marks of $i^{th}$ student in the sample.
Y : student of class.
$Y_i$ : Maths marks of $i^{th}$ student in the class.
$\overline{y}=\dfrac{1}{n}\sum_{i=1}^{n}y_i$ : Average of sample class.
$\overline{Y}=\dfrac{1}{N}\sum_{i=1}^{N}Y_i$ : Average of whole class.
$S^2 = \dfrac{1}{N-1} \sum_{i=1}^{N} (Y_i-\bar{Y})^2$ : S=Std dev of the class.
$\sigma^2=\dfrac{1}{N} \sum_{i=1}^{N} (Y_i-\bar{Y})^2$ : Variance of the class.
Standard error of sample mean $SE_{mean}=\dfrac{s}{\sqrt{n}}$.\\
Where 
\begin{align*}
s & = \text{standard deviation of sample mean.}\\
n & = \text{sample class size.}
\end{align*}
\textbf{Variance of the $\overline{y}$}
\begin{align}
& V(\overline{y})= E(\overline{y}-\overline{Y})^2\\
& = E\left[\dfrac{1}{n} \sum_{i=1}^{n}(y_i-\overline{Y})\right]^2\\
& = E\left[\dfrac{1}{n^2} \sum_{i=1}^{n} (y_i-\overline{Y})^2 + \dfrac{1}{n^2} \underset{1\leq i\neq j\leq n}{\sum\sum}\, (y_i-\overline{Y})(y_j-\overline{Y})\right]\\
& = \dfrac{1}{n^2}\sum_{i=1}^{n} E(y_i-\overline{Y})^2+\dfrac{1}{n^2} \underset{1\leq i\neq j\leq n}{\sum\sum}\, E(y_i-\overline{Y})(y_j-\overline{Y})\\
& \text{Let } K=\underset{1\leq i\neq j\leq n}{\sum\sum}\, E(y_i-\overline{Y})(y_j-\overline{Y})\\
& = \dfrac{1}{n^2}\sum_{i=1}^{n} \sigma^2 + \dfrac{K}{n^2}\\
& = \dfrac{1}{n^2} n \sigma^2 +\dfrac{K}{n^2}\\
& = \dfrac{N-1}{Nn} S^2+\dfrac{K}{n^2}\label{june2018-58:eq_1}
\end{align}
Finding the value of K in case of Simple random sampling with repetition (SRSWR)and Simple random sampling without repetition(SRSWOR) allows us to calculate the variance of mean.
\vspace{0.5 cm}
\textbf{K value in case of SRSWOR}
\begin{align*}
&K=\underset{1\leq i\neq j\leq n}{\sum\sum}\, E(y_i-\overline{Y})(y_j-\overline{Y})
\end{align*}
Consider
\begin{multline*}
E(y_i-\overline{Y})(y_j-\overline{Y})= \\
\dfrac{1}{N(N-1)}\underset{1\leq k\neq l\leq n}{\sum\sum}\, E(y_k-\overline{Y})(y_l-\overline{Y})
\end{multline*}
Since
\begin{multline*}
\left[\sum_{k=1}^N(y_k-\overline{Y})\right]^2=\sum_{i=1}^{N}(y_k-\overline{Y})^2+\\
\underset{1\leq k\neq l\leq n}{\sum\sum}\, E(y_k-\overline{Y})(y_l-\overline{Y})
\end{multline*}
\begin{align*}
&\implies 0 = (N-1)S^2+\underset{1\leq k\neq l\leq n}{\sum\sum}\, E(y_k-\overline{Y})(y_l-\overline{Y})\\
& \implies E(y_i-\overline{Y})(y_j-\overline{Y})=\dfrac{1}{N(N-1)}(N-1)(-S^2)\\
& \implies K = n(n-1)\dfrac{(-S^2)}{N}
\end{align*}
Putting this value in (\ref{june2018-58:eq_1}) gives us 
\begin{align}
V(\overline{y})_{WOR} & = \dfrac{N-1}{Nn} S^2+ \dfrac{n-1(-S^2)}{Nn}\\
& = \dfrac{N-n}{Nn} S^2 \label{june2018-58:eq_2}
\end{align}
\textbf{K value in case of SRSWR}
\begin{align*}
&K=\underset{1\leq i\neq j\leq n}{\sum\sum}\, E(y_i-\overline{Y})(y_j-\overline{Y})
\end{align*}
Since we are selecting the samples with replacements choosing $i^{th}$ and $j^{th}$ sample is independent of each other. So,
\begin{align*}
K&=\underset{1\leq i\neq j\leq n}{\sum\sum}\, E(y_i-\overline{Y})E(y_j-\overline{Y})\\
& = 0\\
& \text{(Since deviation about mean is 0)}
\end{align*}
Putting K=0 in (\ref{june2018-58:eq_1}) we get 
\begin{align}
V(\overline{y})_{WR} & = \dfrac{N-1}{Nn} S^2\label{june2018-58:eq_3}
\end{align}
From equation \eqref{june2018-58:eq_2}  standard error of mean of sample class without repetition
\begin{align}
{SE}_{WOR} & = \dfrac{s}{\sqrt{n}}\\
& = \sqrt{\dfrac{V(\overline{y})_{WOR}}{n}}\\
& = \sqrt{\dfrac{N-n}{Nn^2}}S \label{june2018-58:eq_4}
\end{align} 
From equation \eqref{june2018-58:eq_3}  standard error of mean of sample class with repetition
\begin{align}
{SE}_{WR} & = \sqrt{\dfrac{V(\overline{y})_WR}{n}}\\
& = \sqrt{\dfrac{N-1}{Nn^2}}S \label{june2018-58:eq_5}
\end{align}
Given to find the value of n if $2 \times {SE}_{WOR} =  {SE}_{WR}$.
From \eqref{june2018-58:eq_4} and \eqref{june2018-58:eq_5} we can write 
\begin{align}
& 2\sqrt{\dfrac{N-n}{Nn^2}}S= \sqrt{\dfrac{N-1}{Nn^2}}S\\
\implies & 4(N-n) = N-1\\
\implies & 4N+1-N=4n\\
\implies & 4n=3(125)+1\\
\implies & n=94
\end{align}
Therefore the sample size for the given condition to be met is n=94.(\textbf{Option D})
