\renewcommand{\theequation}{\theenumi}
\renewcommand{\thefigure}{\theenumi}
\renewcommand{\thetable}{\theenumi}
\begin{enumerate}[label=\thesection.\arabic*.,ref=\thesection.\theenumi]
\numberwithin{equation}{enumi}
\numberwithin{figure}{enumi}
\numberwithin{table}{enumi}

\item Suppose the random varible $X$ has the following probability density function
\begin{align}
f(x)=
\begin{cases}
\alpha(x-\mu)^{\alpha-1}e^{-(x-\mu)^\alpha} &x>\mu\\
0 &x\leq\mu,
\end{cases}
\end{align}
Where $\alpha>0, -\infty<\mu<\infty$. Which of the following statements are correct? The Hazard function of $X$ is
\begin{enumerate}[label=\alph*)]
\item an increasing function for all $\alpha>0$
\item a decreasing function for all $\alpha>0$
\item an increasing function for some $\alpha>0$
\item a decreasing function for some $\alpha>0$
\end{enumerate}
%
\solution
\input{variable/solutions/1/Assignment3.tex}



\item Consider the function \textit{f(x)} defined as \textit{f(x)} = \textit{ce$^{-x^{4}}$}, $\textit{x} \in R$ . For what value of \textit{c} is \textit{f} a probability density function?\\
\begin{enumerate}
    \item $\displaystyle\frac{2}{\Gamma(1/4)}$\\\label{june/2019/52/option 1}
    \item $\displaystyle\frac{4}{\Gamma(1/4)}$\\
    \item $\displaystyle\frac{3}{\Gamma(1/3)}$\\
    \item $\displaystyle\frac{1}{4\Gamma(4)}$
\end{enumerate}
%
\solution
\input{solutions/2019/52.tex}

\item Let X and Y be i.i.d random variables uniformly distributed on (0,4).Then \pr{X>Y|X<2Y} is
\begin{enumerate}
    \item 1/3
    \item 5/6
    \item 1/4
    \item 2/3
\end{enumerate}
\solution
\input{solutions/2018/dec/50.tex}
%
\item Suppose $X$ is a positive random variable with the following probability density function,
\begin{align*}
f(x) = (\alpha x^{\alpha -1} + \beta x^{\beta-1} ) e^{-x^{\alpha}-x^{\beta}} ; x>0
\end{align*}
for $ \alpha >0, \beta >0$.
Then the hazard function of $X$ for some choices of $\alpha$ and $\beta$ can be
\begin{enumerate}
    \item an increasing function.
    \item a decreasing function.
    \item a constant function.
    \item a non monotonic function
\end{enumerate}
%
\solution
\input{solutions/2018/dec/118/Assignment7.tex}
%
\item Suppose the random variable X has the following probability density funtion 
\begin{align}
    f(x)=\begin{cases}\alpha\brak{x-\mu}^{\alpha -1}e^{-\brak{x-\mu}^\alpha};&x>\mu\\
                        0                               &x\leq\mu    
    \end{cases}\nonumber
\end{align}
where $\alpha>0,-\infty <\mu<\infty$. Which of the following are correct? The hazard function of $X$ is
\begin{enumerate}
    \item an increasing function for all $\alpha>0$
    \item a decreasing function for all $\alpha >0$
    \item an increasing function for some $\alpha>0$
    \item a decreasing function for some $\alpha>0$
\end{enumerate}
%
\solution
\input{./solutions/2017/june/118/Assignment5.tex}
%
%
\item Let $X$ be a random variable with a certain non-degenerate distribution. Then identify the correct statements
\begin{enumerate}
    \item If $X$ has an exponential distribution then $median\brak{X}<E\brak{X}$
    \item If $X$ has a uniform distribution on an interval $[a,b]$, then $E\brak{X}<median\brak{X}$
    \item If $X$ has a Binomial distribution then $V\brak{X}<E\brak{X}$
    \item If $X$ has a normal distribution, then $E\brak{X}<V\brak{X}$
\end{enumerate}
%
\solution
\input{solutions/2016/dec/107.tex}
%
\item A fair coin is tossed repeatedly. Let $X$ be the number of tails before the first heads occurs. Let $Y$ denote the number of tails between the first and second heads. Let $X+Y = N$. Then which of the following are true?
\begin{enumerate}
    \item X and Y are independent random variables with
    {\footnotesize
    \begin{align}
        \pr{X = k} = \pr{Y = k} =
        \begin{cases}
            2^{-(k+1)} & k=0,1,2 \ldots
            \\
            0 & otherwise
        \end{cases}
    \end{align}
    }
    \item $N$ has a probability mass function given by
    {\small
     \begin{align}
        \pr{N = k} =
        \begin{cases}
            (k-1)2^{-k} & k=2,3,4 \ldots
            \\
            0 & otherwise
        \end{cases}
    \end{align}
    }
    \item Given $N = n$, the conditional distribution of X and Y are independent
    \item Given $N = n$
     \begin{align}
        \pr{X = k} =
        \begin{cases}
            \frac{1}{n+1} & n=0,1,2 \ldots
            \\
            0 & otherwise
        \end{cases}
    \end{align}
\end{enumerate}
%

\item Assume that $X\sim Binomial(n, p)$ for some $n\geq 1$ and $0<p<1$
and $Y\sim poisson(\lambda)$for some $\lambda > 0$.Suppose E[X]=E[Y].Then
\begin{enumerate}
    \item $var(X)=Var(Y)$\\
    \item $var(X)<Var(Y)$\\
    \item $var(Y)<Var(X)$\\
    \item $Var(X)$ may be larger or smaller than $Var(Y)$ depending on the values of n,p and $\lambda$
\end{enumerate}
%
%
\solution
\input{solutions/2015/june/53.tex}
%
%
\item Let $X$ be a non-negative integer valued random variable with probability mass function $f(x)$ satisfying $(x+1)f(x+1)=(\alpha + \beta x)f(x)$, $x=0,1,2,...$; $\beta \neq 1$. You may assume that $E(X)$ and $Var(X)$ exist. Then which of the following statements are true?

\begin{enumerate}
    \item $E(X)=\dfrac{\alpha}{1-\beta}$ \vspace{0.2cm}
    \item $E(X)=\dfrac{\alpha^2}{(1-\beta)(1+\alpha)}$ \vspace{0.2cm}
    \item $Var(X)=\dfrac{\alpha^2}{(1-\beta)^2}$ \vspace{0.2cm}
    \item $Var(X)=\dfrac{\alpha}{(1-\beta)^2}$
\end{enumerate}
%
\solution
\input{solutions/2013/june/75.tex}
%
\item Let X be a random variable with probability density function,
\begin{align}
    f(x)=\alpha(x-\mu)^{\alpha-1}e^{-(x-\mu)^{\alpha}}
\end{align}
such that $-\infty<\mu<\infty\;;\alpha>0\;;x>\mu$, The hazard function is: 
\begin{enumerate}
    \item constant for all $\alpha$
    \item an increasing function for some $\alpha$
    \item independent of $\alpha$
    \item independent of $\mu$ when $\alpha=1$
\end{enumerate}
%
\solution
\input{solutions/2013/june/71.tex}
%
\item 
A point is chosen at random from a circular disc shown below. What is the probability that the point lies in the sector OAB?\\

\begin{tikzpicture}
\draw (0,0) circle (3cm);
\draw (0,0) node{O}-- (2,2.25) node{A};
\draw (0,0) -- (2.828,1) node{B};
\end{tikzpicture}\\

( where $\angle$AOB = x radians )


    \begin{enumerate}
        \item $\frac{2x}{\pi}$
        \item $\frac{x}{\pi}$
        \item $\frac{x}{2\pi}$
        \item $\frac{x}{4\pi}$
    \end{enumerate}

%
\solution
\input{solutions/2013/june/16/Assignment6.tex}
%
\item Let $X$ and $Y$ be independent random variables each following a uniform distribution on $(0,1)$.Let $W=XI_{\{Y\leq X^2\}}$,where $I_A$ denotes the indicator function of set $A$.Then which of the following statements are true? \\
\begin{enumerate}
\item The cumulative distribution function of $W$ is given by
\begin{align}
  F_W(t)=t^2I_{\{0\leq t \leq 1\}}+ I_{\{t > 1\}}
\end{align}
\item $P\sbrak{W>0}=\frac{1}{3}$
\item The cumulative distribution function of $W$ is continuous
\item The cumulative distribution function of $W$ is given by
\begin{align}
  F_W(t)=\brak{\frac{2+t^3}{3}}I_{\{0\leq t \leq 1\}}+ I_{\{t > 1\}}
\end{align}
\end{enumerate}
%
\solution
\input{solutions/2013/june/70/assignment8.tex}
%
%
\newcommand{\tikzAngleOfLine}{\tikz@AngleOfLine}
  \def\tikz@AngleOfLine(#1)(#2)#3{%
  \pgfmathanglebetweenpoints{%
    \pgfpointanchor{#1}{center}}{%
    \pgfpointanchor{#2}{center}}
  \pgfmathsetmacro{#3}{\pgfmathresult}%
  }

\item A point is chosen at random from a circular disc shown below. What is the probability that the point lies in the sector OAB?\\
\begin{tikzpicture}[
    colorstyle/.style={
       circle, draw=black,fill=black,
       thick, inner sep=0pt, minimum size=2 mm,
       outer sep=0pt
        },
    scale=2]
\draw (0,0) circle (2cm);
\node at (0,0) [colorstyle,label=below:O]{};
\node at (1,1.732) [colorstyle,label=above:A]{};
\node at (1.732,1) [colorstyle,label=above right:B]{};
\draw (0,0) -- (1,1.732);
\draw (0,0) -- (1.732,1);
\coordinate (O) at (0,0);
\coordinate (A) at (1,1.732);
\coordinate (B) at (1.732,1);
\tikzAngleOfLine(O)(B){\AngleStart}
    \tikzAngleOfLine(O)(A){\AngleEnd}
    \draw[red,<->] (O)+(\AngleStart:1cm) arc (\AngleStart:\AngleEnd:1 cm);
    \node[circle,fill=green] at ($(O)+({(\AngleStart+\AngleEnd)/2}:1.5 cm)$) {x};
\end{tikzpicture}\\
( where $\angle$AOB = x radians )
\begin{multicols}{2}
    \begin{enumerate}
        \item $\frac{2x}{\pi}$
        \item $\frac{x}{\pi}$
        \item $\frac{x}{2\pi}$
        \item $\frac{x}{4\pi}$
    \end{enumerate}
\end{multicols}
%
\solution
\input{solutions/2013/june/16.tex}

\end{enumerate}