\renewcommand{\theequation}{\theenumi}
\renewcommand{\thefigure}{\theenumi}
\renewcommand{\thetable}{\theenumi}
\begin{enumerate}[label=\thesection.\arabic*.,ref=\thesection.\theenumi]
\numberwithin{equation}{enumi}
\numberwithin{figure}{enumi}
\numberwithin{table}{enumi}


\item \textbf{Step 1.} Flip a coin twice.\\
\textbf{Step 2.} If the outcomes are (TAILS, HEADS) then output Y and stop.\\
\textbf{Step 3.} If the outcomes are either (HEADS, HEADS) or (HEADS, TAILS), then output N and stop.\\
\textbf{Step 4.} If the outcomes are (TAILS, TAILS), then go to Step 1.\\
The probability that the output of the experiment is Y is (upto two decimal places)......
%
\solution
\input{markov/solutions/1.tex}
%
\item Consider a simple symmetric random walk on integers ,Where from every state i you to move to i-1 and i+1 with  probability half each. Then which of the following are correct?
\begin{enumerate}
    \item The random walk is aperiodic
    \item The random walk is irreducible
    \item The random walk is null recurrent 
    \item The random walk is positive recurrent 
\end{enumerate}
%
\solution
\input{solutions/2019/105.tex}



\item Consider a Markov Chain with state space $\cbrak{0,1,2}$ and transition matrix
\begin{align}
P = 
\begin{blockarray}{c@{\hspace{1pt}}rrr@{\hspace{3pt}}}
         & 0   & 1   & 2 \\
        \begin{block}{r@{\hspace{3pt}}@{\hspace{1pt}}
    (@{\hspace{1pt}}rrr@{\hspace{1pt}}@{\hspace{1pt}})}
        0 & \frac{1}{4} & \frac{5}{8} & \frac{1}{8}  \\[1mm]
        1 & \frac{1}{4} & 0 & \frac{3}{4}  \\[1mm]
        2 &  \frac{1}{2} & \frac{3}{8} & \frac{1}{8}  \\
        \end{block}
    \end{blockarray}
\end{align}
Then which of the following are true?
\begin{enumerate}
\item $\lim_{n \to \infty} p_{12}^{(n)} = 0$
\item $\lim_{n \to \infty} p_{12}^{(n)} = \lim_{n \to \infty} p_{21}^{(n)}$
\item $\lim_{n \to \infty} p_{22}^{(n)} = \frac{1}{8}$
\item $\lim_{n \to \infty} p_{21}^{(n)} = \frac{1}{3}$
\end{enumerate}

%
\item Consider a Markov chain with state space {1,2,....,100}. Suppose states 2i and 2j communicate with each other and states 2i-1 and 2j-1 communicate with each other for every i,j = 1,2,...,50. Further suppose that $p^{(2)}_{3,3}$ > 0,$p^{(3)}_{4,4}$ > 0 and $p^{(7)}_{2,5}$ > 0. Then 
\begin{enumerate}
\item The Markov chain is irreducible.
\item The Markov chain is aperiodic.
\item State 8 is recurrent.
\item State 9 is recurrent.
\end{enumerate}
%
\solution
\input{solutions/2014/dec/106/LaTex/Assignment_7.tex}
%
%
\item A standard fair die is rolled until some face other than 5 or 6 turns up.Let X denote the face value of the last roll.Let A=\{X is even\} and B=\{X is atmost 2\}
Then,
\begin{enumerate}
\begin{multicols}{2}
\setlength\itemsep{1em}
\item $\Pr{(A\cap {B})}=0$\\
\item $\Pr{(A \cap B)}=\frac{1}{6}$\\
\item $\Pr{(A\cap B)}=\frac{1}{4}$\\
\item $\Pr{({A} \cap {B})}=\frac{1}{3}$
\end{multicols}
\end{enumerate}
%
\solution
\input{solutions/2018/june/49.tex}
\item %
Consider a Markov chain with five states $\{1,2,3,4,5\}$ and transition matrix
\begin{align}
    P=\myvec{\frac{1}{2} & 0 & 0 & \frac{1}{2} & 0\\
            0 & \frac{1}{7} & 0 & 0&\frac{6}{7}\\
              \frac{1}{5} & \frac{1}{5} & \frac{1}{5} & \frac{1}{5} & \frac{1}{5}\\ \frac{1}{3} & 0 & 0 & \frac{2}{3} & 0 \\
              0 & \frac{5}{8} & 0 & 0 & \frac{3}{8}}
\end{align}
Which of the following are true?
\begin{enumerate}
\item 3 and 1 are in the same communicating class
\item 1 and 4 are in the same communicating class
\item 4 and 2 are in the same communicating class
\item 2 and 5 are in the same communicating class
\end{enumerate}
%
\solution
\input{./solutions/2017/dec/105/solution.tex}
%\twocolumn 
%
\item $A$ and $B$ play a game of tossing a fair coin. $A$ starts the game by tossing the coin once and $B$ then tosses the coin twice, followed by $A$ tossing the coin once and $B$ tossing the coin twice and this continues until a head turns up. Whoever gets the first head wins the game. Then, 
\begin{enumerate}
    \item $P(B$ Wins) $> P(A$ Wins)
    \item $P(B$ Wins) $= 2P(A$ Wins)
    \item $P(A$ Wins) $> P(B$ Wins)
    \item $P(A$ Wins) $= 1-P(B$ Wins)
\end{enumerate}
%
%
\solution
\input{solutions/2016/dec/104.tex}
\item Consider a Markov chain with state space {1,2,....,100}. Suppose states 2i and 2j communicate with each other and states 2i-1 and 2j-1 communicate with each other for every i,j = 1,2,...,50. Further suppose that $p^{(2)}_{3,3}$ > 0,$p^{(3)}_{4,4}$ > 0 and $p^{(7)}_{2,5}$ > 0. Then 
\begin{enumerate}
\item The Markov chain is irreducible.
\item The Markov chain is aperiodic.
\item State 8 is recurrent.
\item State 9 is recurrent.
\end{enumerate}
\solution
\input{solutions/2014/dec/106/LaTex/Assignment_7.tex}


\end{enumerate}
