\renewcommand{\theequation}{\theenumi}
\renewcommand{\thefigure}{\theenumi}
\begin{enumerate}[label=\thesection.\arabic*.,ref=\thesection.\theenumi]
\numberwithin{equation}{enumi}
\numberwithin{figure}{enumi}
\numberwithin{table}{enumi}

\item The probability that a ticketless traveler is caught during a trip is 0.1. If the traveler makes 4 trips , the probability that he/she will be caught during at least one of the trips is:\\
\begin{enumerate}
    \item $1-(0.9)^4$
    \item $(1-0.9)^4$
    \item $1-(1-0.9)^4$
    \item $(0.9)^4$
\end{enumerate}
\solution
\input{solutions/2015/dec/3.tex}

\item Suppose that $(X,Y)$ has a joint probability distribution with the marginal distribution of $X$ being N(0,1) and $E(Y|X=x)=x^3$ for all $x \in R$. Then, which of the following statements are true?
\begin{enumerate}
    \item Corr$(X,Y) = 0$
    \item Corr$(X,Y) > 0$
    \item Corr$(X,Y) < 0$
    \item X and Y are independent
\end{enumerate}
\solution
\input{solutions/2015/dec/108.tex}
%
 \item Let $X_1,X_2,...,X_n$ be independent and identically distributed, each having a uniform distribution on $(0,1)$. Let $S_n=\sum_{i=1}^{n}X_i$ for $n\ge 1$. Then, which of the following statements are true? 
\begin{enumerate}[label=\Alph*)]
\item $\frac{S_n}{n \log{n}}\to 0 \text{ as } n \to \infty$ with probability 1.
\item $\pr{\brak{S_n>\frac{2n}{3}}\text{occurs for infinitely many n}}=1$
\item $\frac{S_n}{\log{n}}\to 0\text{ as } n \to \infty$ with probability 1.
\item $\pr{\brak{S_n>\frac{n}{3}}\text{occurs for infinitely many n}}=1$
\end{enumerate}
%
\solution
\input{solutions/2015/dec/106.tex}
%
\item A fair coin is tossed repeatedly. Let $X$ be the number of tails before the first heads occurs. Let $Y$ denote the number of tails between the first and second heads. Let $X+Y = N$. Then which of the following are true?
\begin{enumerate}
    \item X and Y are independent random variables with
    {\footnotesize
    \begin{align}
        \pr{X = k} = \pr{Y = k} =
        \begin{cases}
            2^{-(k+1)} & k=0,1,2 \ldots
            \\
            0 & otherwise
        \end{cases}
    \end{align}
    }
    \item $N$ has a probability mass function given by
    {\small
     \begin{align}
        \pr{N = k} =
        \begin{cases}
            (k-1)2^{-k} & k=2,3,4 \ldots
            \\
            0 & otherwise
        \end{cases}
    \end{align}
    }
    \item Given $N = n$, the conditional distribution of X and Y are independent
    \item Given $N = n$
     \begin{align}
        \pr{X = k} =
        \begin{cases}
            \frac{1}{n+1} & n=0,1,2 \ldots
            \\
            0 & otherwise
        \end{cases}
    \end{align}
\end{enumerate}
%
\item An urn has 3 red and 6 black balls. Balls are drawn at random one by one without replacement. The probability that second red ball appears on fifth draw is: \\
\begin{enumerate}
    \item $\frac{1}{9!}$
    \newline
    \item $\frac{4!}{9!}$
    \newline
    \item $4\brak{\frac{6!4!}{9!}}$
    \newline
    \item $\frac{6!4!}{9!}$
\end{enumerate}
%
%
\solution
\input{solutions/2015/dec/104.tex}
%
\item Let $X_i 's$ be independent random variables such that $X_i 's$ are symmetric about 0 and $var(X_i)=2i - 1$,for $i\geq 1$.then,
$\lim_{n \to \infty}\pr{X_1 +X_2 + \dots + X_n > n\log{n}}$
\begin{enumerate}
\begin{multicols}{2}
\setlength\itemsep{2em}
\item does not exist.
\item equals $\dfrac{1}{2}$.\\
\item equals 1.
\item equals 0.
\end{multicols}
\end{enumerate}
%
\solution
\input{solutions/2015/dec/53.tex}
%
\item Suppose
$\begin{pmatrix}
X\\
Y
\end{pmatrix}$ is a random vector such that the marginal distribution of $X$ and the marginal distribution of $Y$ are the same and each is normally distributed with mean 0 and variance 1. Then, which of the following conditions imply independence of $X$ and $Y?$
\begin{enumerate}
\item Cov$\brak{X,Y}=0$
\item $aX+bY$ is normally distributed with mean 0 and variance $a^2+b^2$ for all real $a$ and $b$
\item $\pr{X\le 0, Y\le0}=\frac{1}{4}$
\item $E\sbrak{e^{itX+isY}}=E\sbrak{e^{itX}}E\sbrak{e^{isY}}$ for all real $s$ and $t$
\end{enumerate}
%
\solution
\input{solutions/2015/dec/109/main.tex}

\end{enumerate}
