\renewcommand{\theequation}{\theenumi}
\renewcommand{\thefigure}{\theenumi}
\renewcommand{\thetable}{\theenumi}
\begin{enumerate}[label=\thesection.\arabic*.,ref=\thesection.\theenumi]
\numberwithin{equation}{enumi}
\numberwithin{figure}{enumi}
\numberwithin{table}{enumi}

\item $X_1,X_2,\ldots,X_n$ are independent and identically
distributed as $N(\mu, \sigma^2)$, $-\infty < \mu < \infty$, $\sigma^2 > 0$. Then
\begin{enumerate}
    \item $\sum_1^n\frac{(X_i-\bar{X})^2}{n-1}$ is the Minimum Variance Unbiased Estimate of $\sigma^2$\\
    \item $\sqrt{\sum_1^n\frac{(X_i-\bar{X})^2}{n-1}}$ is the Minimum Variance Unbiased Estimate of $\sigma$\\
    \item $\sum_1^n\frac{(X_i-\bar{X})^2}{n}$ is the Maximum Likelihood Estimate of $\sigma^2$\\
    \item $\sqrt{\sum_1^n\frac{(X_i-\bar{X})^2}{n}}$ is the Maximum Likelihood \qquad Estimate of $\sigma$
\end{enumerate}
%
\solution
\input{solutions/2016/dec/109.tex}
%
\item There are two boxes. Box-$1$ contains $2$ red balls and $4$ green balls. Box-$2$ contains $4$ red balls and $2$ green balls. A box is selected at random and a ball is chosen randomly from the selected box. If the ball turns out to be red, what is the probability that Box-$1$ had been selected?
%
\solution
\input{solutions/2016/dec/49.tex}
%
\item Suppose customers arrive in a shop according to a Poisson process with rate $4$ per hour. The shop opens at $10:00$ am. If it is given that the second customer arrives at $10:40 $ am, what is the probability that no customer arrived before $10:30 $ am? 
%
    \begin{enumerate}
        \item $\frac{1}{4}$
        \item $e^{-2}$
        \item $\frac{1}{2}$
        \item $e^{\frac{1}{2}}$
    \end{enumerate}
%
%
\solution
\input{solutions/2016/dec/51.tex}
%
\item A fair die is thrown two times independently. Let $X,Y$ be the outcomes of these two throws and $Z=X+Y$. Let $U$ be the remainder obtained when $Z$ is divided by 6. Then which of the following statement(s) is/are true?
\begin{enumerate}
    \item $X$ and $Z$ are independent \label{option 1}
    \item $X$ and $U$ are independent \label{option 2}
    \item $Z$ and $U$ are independent \label{option 3}
    \item $Y$ and $Z$ are not independent \label{option 4}
\end{enumerate}
%
\solution
\input{solutions/2016/dec/103.tex}

%\item Consider a Markov Chain with state space $\cbrak{0,1,2}$ and transition matrix
%\begin{align}
%P = 
%\begin{blockarray}{c@{\hspace{1pt}}rrr@{\hspace{3pt}}}
%         & 0   & 1   & 2 \\
%        \begin{block}{r@{\hspace{3pt}}@{\hspace{1pt}}
%    (@{\hspace{1pt}}rrr@{\hspace{1pt}}@{\hspace{1pt}})}
%        0 & \frac{1}{2} & \frac{1}{2} & 0  \\
%        1 & 0 &\frac{1}{2}  & \frac{3}{4}  \\
%%
%        2 &  \frac{1}{3} & \frac{1}{3} & \frac{1}{3}  \\
%        \end{block}
%    \end{blockarray}
%\end{align}
%For any two states $i$ and $j$, let $p_{ij}^{(n)}$ denote the $n$-step transition probability of going from $i$ to $j$.  Identify correct statements.
%\begin{enumerate}
%\item $\lim_{n \to \infty} p_{11}^{(n)} = \frac{2}{9}$
%\item $\lim_{n \to \infty} p_{21}^{(n)} = 0$
%\item $\lim_{n \to \infty} p_{32}^{(n)} = \frac{1}{3}$
%\item $\lim_{n \to \infty} p_{13}^{(n)} = \frac{1}{3}$
%\end{enumerate}

\end{enumerate}
