\renewcommand{\theequation}{\theenumi}
\renewcommand{\thefigure}{\theenumi}
\renewcommand{\thetable}{\theenumi}
\begin{enumerate}[label=\thesection.\arabic*.,ref=\thesection.\theenumi]
\numberwithin{equation}{enumi}
\numberwithin{figure}{enumi}
\numberwithin{table}{enumi}
%
\item Let $X$ be a non-negative integer valued random variable with probability mass function $f(x)$ satisfying $(x+1)f(x+1)=(\alpha + \beta x)f(x)$, $x=0,1,2,...$; $\beta \neq 1$. You may assume that $E(X)$ and $Var(X)$ exist. Then which of the following statements are true?

\begin{enumerate}
    \item $E(X)=\dfrac{\alpha}{1-\beta}$ \vspace{0.2cm}
    \item $E(X)=\dfrac{\alpha^2}{(1-\beta)(1+\alpha)}$ \vspace{0.2cm}
    \item $Var(X)=\dfrac{\alpha^2}{(1-\beta)^2}$ \vspace{0.2cm}
    \item $Var(X)=\dfrac{\alpha}{(1-\beta)^2}$
\end{enumerate}
%
\solution
\input{solutions/2013/june/75.tex}
%
\item Let X be a random variable with probability density function,
\begin{align}
    f(x)=\alpha(x-\mu)^{\alpha-1}e^{-(x-\mu)^{\alpha}}
\end{align}
such that $-\infty<\mu<\infty\;;\alpha>0\;;x>\mu$, The hazard function is: 
\begin{enumerate}
    \item constant for all $\alpha$
    \item an increasing function for some $\alpha$
    \item independent of $\alpha$
    \item independent of $\mu$ when $\alpha=1$
\end{enumerate}
%
\solution
\input{solutions/2013/june/71.tex}
%
\item 
A point is chosen at random from a circular disc shown below. What is the probability that the point lies in the sector OAB?\\

\begin{tikzpicture}
\draw (0,0) circle (3cm);
\draw (0,0) node{O}-- (2,2.25) node{A};
\draw (0,0) -- (2.828,1) node{B};
\end{tikzpicture}\\

( where $\angle$AOB = x radians )


    \begin{enumerate}
        \item $\frac{2x}{\pi}$
        \item $\frac{x}{\pi}$
        \item $\frac{x}{2\pi}$
        \item $\frac{x}{4\pi}$
    \end{enumerate}

%
\solution
\input{solutions/2013/june/16/Assignment6.tex}
%
\item Let $X$ and $Y$ be independent random variables each following a uniform distribution on $(0,1)$.Let $W=XI_{\{Y\leq X^2\}}$,where $I_A$ denotes the indicator function of set $A$.Then which of the following statements are true? \\
\begin{enumerate}
\item The cumulative distribution function of $W$ is given by
\begin{align}
  F_W(t)=t^2I_{\{0\leq t \leq 1\}}+ I_{\{t > 1\}}
\end{align}
\item $P\sbrak{W>0}=\frac{1}{3}$
\item The cumulative distribution function of $W$ is continuous
\item The cumulative distribution function of $W$ is given by
\begin{align}
  F_W(t)=\brak{\frac{2+t^3}{3}}I_{\{0\leq t \leq 1\}}+ I_{\{t > 1\}}
\end{align}
\end{enumerate}
%
\solution
\input{solutions/2013/june/70/assignment8.tex}
%
\item Let $U_1,U_2\dots,U_n$ be independent and identically distributed random variables each
having a uniform distribution on (0,1). Then,$\lim_{n \to +\infty} \pr{U_1+U_2\dots,U_n\leq \frac{3}{4}n}$
\begin{enumerate}
    \item does not exist
    \item exists and equals 0
    \item exists and equals 1
    \item exists and equals $\frac{3}{4}$
\end{enumerate}
%
\solution
\input{solutions/2013/june/59.tex}
%
\item  Consider the quadratic equation $x^2+2U x+V=0$ where $U$ and $V$ are chosen independently and randomly from $\{1,2,3\}$ with equal probabilities. Then probability that the equation has both roots real
\begin{enumerate}
    \item $\frac{2}{3}$
    \item $\frac{1}{2}$
    \item $\frac{7}{9}$
    \item $\frac{1}{3}$
\end{enumerate}
%
\solution
\input{solutions/2013/june/60.tex}
%
\newcommand{\tikzAngleOfLine}{\tikz@AngleOfLine}
  \def\tikz@AngleOfLine(#1)(#2)#3{%
  \pgfmathanglebetweenpoints{%
    \pgfpointanchor{#1}{center}}{%
    \pgfpointanchor{#2}{center}}
  \pgfmathsetmacro{#3}{\pgfmathresult}%
  }

\item A point is chosen at random from a circular disc shown below. What is the probability that the point lies in the sector OAB?\\
\begin{tikzpicture}[
    colorstyle/.style={
       circle, draw=black,fill=black,
       thick, inner sep=0pt, minimum size=2 mm,
       outer sep=0pt
        },
    scale=2]
\draw (0,0) circle (2cm);
\node at (0,0) [colorstyle,label=below:O]{};
\node at (1,1.732) [colorstyle,label=above:A]{};
\node at (1.732,1) [colorstyle,label=above right:B]{};
\draw (0,0) -- (1,1.732);
\draw (0,0) -- (1.732,1);
\coordinate (O) at (0,0);
\coordinate (A) at (1,1.732);
\coordinate (B) at (1.732,1);
\tikzAngleOfLine(O)(B){\AngleStart}
    \tikzAngleOfLine(O)(A){\AngleEnd}
    \draw[red,<->] (O)+(\AngleStart:1cm) arc (\AngleStart:\AngleEnd:1 cm);
    \node[circle,fill=green] at ($(O)+({(\AngleStart+\AngleEnd)/2}:1.5 cm)$) {x};
\end{tikzpicture}\\
( where $\angle$AOB = x radians )
\begin{multicols}{2}
    \begin{enumerate}
        \item $\frac{2x}{\pi}$
        \item $\frac{x}{\pi}$
        \item $\frac{x}{2\pi}$
        \item $\frac{x}{4\pi}$
    \end{enumerate}
\end{multicols}
%
\solution
\input{solutions/2013/june/16.tex}
%
\item Consider a parallel system with two components. The lifetimes of the two components are independent and identically distributed random variables each following an exponential distribution with mean 1. The expected lifetime of the system is:
\begin{enumerate}[label=\Alph*)]
    \item $1$\\[0.5pt]
    \item $\dfrac{1}{2}$\\
    \item $\dfrac{3}{2}$\\
    \item $2$
\end{enumerate}
%
\solution
\input{solutions/2013/june/42/Assignment7.tex}
%
\item Let $X_1$,$X_2$,... be independent random variables each following exponential distribution with mean 1. Then which of the following statements are correct?
\begin{enumerate}
    \item P($X_n > \log n$ for infinitely many $n \geq 1$) = 1
    \item P($X_n > 2$ for infinitely many $n \geq 1$) = 1
    \item P($X_n > \frac{1}{2}$ for infinitely many $n \geq 1$) = 0
    \item P($X_n > \log n, X_{n+1}>\log (n+1)$ for infinitely many $n \geq 1$) = 0
\end{enumerate}
%
\solution
\input{solutions/2013/june/101.tex}
%
\item Suppose $X_1$ and $X_2$ are independent and identically distributed random variables each following an exponential distribution with mean $\theta$, i.e., the common pdf is given by $f_\theta(x) = \frac{1}{\theta}e^{\frac{-x}{\theta}}, 0<x<\infty,0<\theta<\infty.$ Then which of the following is true? Conditional distribution of $X_2$ given $X_1+X_2=t$ is 
\begin{enumerate}
    \item exponential with mean $\frac{t}{2}$ and hence $X_1+X_2$ is sufficient for $\theta$ \label{june/2013/40/option 1}
    \item exponential with mean $\frac{t\theta}{2}$ and hence $X_1+X_2$ is not sufficient for $\theta$ \label{june/2013/40/option 2}
    \item uniform$(0,t)$ and hence $X_1+X_2$ is sufficient for $\theta$ \label{june/2013/40/option 3}
    \item uniform$(0,t\theta)$ and hence $X_1+X_2$ is not sufficient for $\theta$ \label{june/2013/40/option 4}
\end{enumerate}
%
\solution
\input{solutions/2013/june/40.tex}
%
\item Let $X_{1},X_{2},\dots$ be independent and identically distributed random variables each following a uniform distribution on (0,1). Denote $T_{n}=max\{ X_{1},X_{2},\dots,X_{n}\}$. Then, which of the following statements are true?
\begin{enumerate}
    \item $T_{n}$ converges to 1 in probability.
    \item $n(1-T_{n})$ converges in distribution.
    \item $n^{2}(1-T_{n})$ converges in distribution.
    \item $\sqrt{n}(1-T_{n})$ converges to 0 in probability.
\end{enumerate}
%
\solution
\input{solutions/2013/june/72/Assignment9.tex}

\end{enumerate}
